The Exoplanet Orbit Database \textsc{II}: Updates to exoplanets.org

### 2014-07-22 draft/ms.tex
Incorporate Sharon's comments and update Ricker2014 in references.tex

The Exoplanet Orbit Database (EOD) compiles orbital, transit, host star, and other
parameters of robustly detected exoplanets reported in the peer-reviewed
literature. The EOD can be navigated through the Exoplanet Data
Explorer (EDE) Plotter and Table, available on the World Wide Web at exoplanets.org. The EOD contains data for 1490 confirmed exoplanets as of March 2014.  
The EOD descends from a table in \citet{Butler2002} and the Catalog of Nearby Exoplanets \citep{Butler2006}, and the first complete documentation for the EOD and the EDE was presented in 
\cite{Wright2011}. In this work, we describe our work since then.  We have expanded the scope of the
EOD to include secondary eclipse parameters, asymmetric uncertainties,
and expanded the EDE to include
the sample of over 3000 \kepler\ Objects of Interest (KOIs), and other
real planets without good orbital parameters (such as many of those
those detected by microlensing and imaging.) Users can download the
latest version of the entire EOD as a single comma separated value
file from the front page of exoplanets.org.

@@

% Recent development in exoplanet discoveries
Since the launch of NASA's \kepler\ mission \citep{Borucki2010}, the
number of confirmed exoplanets has increased from about 300 to over
1490 as of March 2014. \kepler\ contributed to a majority of these new discoveries ($> 800$) while providing an
additional sample of over 4,000 exoplanet candidates (\kepler\ Objects
of Interest, KOIs; e.g.~\citealt{Batalha2013}). The transit method has thus surpassed the radial velocity (RV) method to become the most fruitful
means of detecting exoplanets. Meanwhile, great promise lies within
the new and future exoplanet surveys and instruments with direct
imaging (e.g., the Gemini Planet Imager, GPI,
\citealt{Macintosh2014}) and microlensing (e.g., the Wide-Field
InfraRed Survey Telescope, WFIRST, \citealt{Green2012}), while the
fronts of RV and transit exoplanet searches keep expanding (e.g., the
MINiature Exoplanet Radial Velocity Array, MINERVA,
\citep{Wright2014}; the Habitable-zone Planet Finder, HPF, \cite{Mahadevan2012} and the
Transiting Exoplanet Survey Satellit, TESS, \citealt{Ricker2014}).

@@

{\bf I} reports the orbital inclination of the planet. Previously, only transiting
systems had $i$ measured, but now some non-transiting systems have
dynamical or astrometric constraints on $i$ (for example, the
microlensing system OGLE-2006-BLG-109L \citep{Bennett2010} and the imaged system, $\beta$ Pictoris \citep{Lagrange2009}).

@@

{\bf SEDEPTHX} whereas X stands for one of ``J", ``H", ``KS", ``KP", ``36", ``45", ``58", ``80":
these fields are the secondary eclipse depth measured in the
corresponding wavelength band. SEDEPTHJ, H, and KS are the depths
measured in the 2MASS wavelength bands in the near infrared, centered
at 1.25~\micron, 1.65~\micron, and 2.15~\micron, respectively. KP is
the depth measured in the \kepler\ photometric band which spans 400 to 865~nm. The other four represent the Spitzer IRAC and MIPS bands centered at
3.6~\micron, 4.5~\micron, 5.8~\micron, and 8.0~\micron.

@@

We provide the brightness of the host star measured in different
filters. We report optical magnitude and color ($V$ and $B-V$),
2MASS $J$, $H$, and $K_s$ magnitudes and, we have added {\bf KP} for
the \kepler\ photometric band. Notes that the definitions of $V$ and $B$ in the literature vary, and are often Hipparcos magnitudes.

@@

If only an upper limit is given, we set the parameter field X to 0,
the uncertainty XU to half of the upper limit, and the upper error bar
XUPPER to the upper limits (same as XUL). For example, if the
literature reports the upper limit for ECC, which we report in ECCUL,
then we set ECC to be 0, ECCUPPER to ECCUL, and UECC to ECCUL/2.  We
are currently implementing a more precise upper limit scheme (see Section~\ref{sec:summary}.)

@@

The following fields do not have associated REF or URL fields. Except
where we record these values directly from discovery papers, {\bf RA},
{\bf DEC}, and PAR are usually from the \textit{Hipparcos}
re-reduction of \cite{van Leeuwen2009}; the $B-V$ ({\bf BMV}) values
are from the \textit{Hipparcos} catalog by \cite{Perryman1997};
stellar magnitudes {\bf J}, {\bf H}, and {\bf KS} (i.e.\ $K_{\rm s}$)
are from the 2MASS catalog
\citep{Skrutskie2006} (as reported in SIMBAD) and the {\bf KP} (i.e.\ $K_P$) magnitudes are from the Exoplanet
Archive \citep{Akeson2013}.

@@

%------------------------------------------------------------------------------
% Figure: single planet page
\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{fig/wasp-14b.eps}
\caption{An example page for an individual exoplanet (WASP-14b in this
  case). The numbers listed in each field contain links to the
  reference on NASA ADS. In this example for WASP-14b, we provide the plot
  for the phased RVs, but we have yet to implement such feature for all
  planets with available RV data.}
\label{fig:individual}
\end{figure}

@@

%------------------------------------------------------------------------------
% Figure: single planet page
\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{fig/mass-per-interactive.eps}
\caption{
  An example plot produced by the interactive plotting tools of
  EDE on exoplanets.org. The interactive plotting interface is shown
  on the right, with the mass-period plot shown on the left. The
  $x$-axis is planet orbital period in days and $y$-axis is planet
  mass in Earth's mass. The exoplanet samples being plotted are the
  ones in the EOD, including transit planets (blue large dots), RV
  planets (red triangles), and timing planets (magenta squares). The
  KOIs are plotted as black small dots, and their masses are
  calculated using their radii based on mass-radius relations from the
  literature (see Section~\ref{sec:orbit}).  Note the
  apples-to-oranges comparison enabled by the hybrid MASS field on the y-axis, which blends estimated
  masses, minimum masses, and true masses on a single plot.}
\label{fig:koi}
\end{figure}

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{fig/senew.eps}
\caption{An example plot that demonstrates the current secondary
  eclipse measurements. Each planet has a set of circles that stand
  for its available secondary eclipse measurements in the database,
  including Spitzer 8.0, 5.8, 4.5, \& 3.6 $\mu m$, and  ground-based
  $J$, $H$, and $Ks$ bands. \kepler\ secondary eclipse measurements
  are labeled as solid black dots. A few representative planets are
  also annotated (a feature not offered by the EDE Plotter, but
  trivially implemented by other image or presentation software).}
\label{fig:se}
\end{figure}

>>>>

The Exoplanet Orbit Database (EOD) compiles orbital, transit, host
star, and other parameters of robustly detected exoplanets reported in
the peer-reviewed literature. The EOD can be navigated through the
Exoplanet Data Explorer (EDE) Plotter and Table, available on the
World Wide Web at exoplanets.org. The EOD contains data for 1492
confirmed exoplanets as of July 2014.  The EOD descends from a table
in \citet{Butler2002} and the Catalog of Nearby Exoplanets
\citep{Butler2006}, and the first complete documentation for the EOD
and the EDE was presented in \cite{Wright2011}. In this work, we
describe our work since then.  We have expanded the scope of the EOD
to include secondary eclipse parameters, asymmetric uncertainties, and
expanded the EDE to include the sample of over 3000 \kepler\ Objects
of Interest (KOIs), and other real planets without good orbital
parameters (such as many of those those detected by microlensing and
imaging.) Users can download the latest version of the entire EOD as a
single comma separated value file from the front page of
exoplanets.org.

@@

% Recent development in exoplanet discoveries
Since the launch of NASA's \kepler\ mission \citep{Borucki2010}, the
number of confirmed exoplanets has increased from about 300 to over
1490 as of July 2014. \kepler\ contributed to a majority of these new
discoveries ($> 800$) while providing an additional sample of over
3,000 exoplanet candidates (\kepler\ Objects of Interest, KOIs;
e.g.~\citealt{Batalha2013}). The transit method has thus surpassed the
radial velocity (RV) method to become the most fruitful means of
detecting exoplanets. Meanwhile, great promise lies within the new and
future exoplanet surveys and instruments with direct imaging (e.g.,
the Gemini Planet Imager, GPI, \citealt{Macintosh2014}) and
microlensing (e.g., the Wide-Field InfraRed Survey Telescope, WFIRST,
\citealt{Green2012}), while the fronts of RV and transit exoplanet
searches keep expanding (e.g., the MINiature Exoplanet Radial Velocity
Array, MINERVA, \citealt{Wright2014}; the Habitable-zone Planet Finder,
HPF, \citealt{Mahadevan2012} and the Transiting Exoplanet Survey
Satellit, TESS, \citealt{Ricker2014}).

@@

{\bf I} reports the orbital inclination of the planet. Previously,
only transiting systems had $i$ measured, but now some non-transiting
systems have dynamical or astrometric constraints on $i$ (for example,
the microlensing system OGLE-2006-BLG-109L by \citealt{Bennett2010}
and the imaged system, $\beta$ Pictoris by \citealt{Lagrange2009}).

@@

{\bf SEDEPTHX} whereas X stands for one of ``J", ``H", ``KS", ``KP",
``36", ``45", ``58", ``80": these fields are the secondary eclipse
depth measured in the corresponding wavelength band. SEDEPTHJ, H, and
KS are the depths measured in the 2MASS wavelength bands in the near
infrared, centered at 1.25~\micron, 1.65~\micron, and 2.15~\micron,
respectively. KP is the depth measured in the \kepler\ photometric
band which spans 400 to 865~nm. The other four represent the
\spitzer\ IRAC bands centered at 3.6~\micron, 4.5~\micron,
5.8~\micron, and 8.0~\micron.

@@

We provide the brightness of the host star measured in different
filters. We report optical magnitude and color ($V$ and $B-V$),
2MASS $J$, $H$, and $K_s$ magnitudes and, we have added {\bf KP} for
the \kepler\ photometric band. Note that the definitions of $V$ and $B$ in the literature vary, and are often Hipparcos magnitudes.

@@

If only an upper limit is given, we set the parameter field X to 0,
and store the upper limit value in the field XUL. The uncertainty UX
is set to half of the upper limit, and the upper error bar XUPPER to
the upper limit value. For example, if the literature reports the
upper limit for ECC, which we report in ECCUL, then we set ECC to be
0, ECCUPPER to ECCUL, and UECC to ECCUL/2.  We are currently
implementing a more precise upper limit scheme (see
Section~\ref{sec:summary}.)

@@

The following fields do not have associated REF or URL fields. Except
where we record these values directly from discovery papers, {\bf RA},
{\bf DEC}, and {\bf PAR} are usually from the \textit{Hipparcos}
re-reduction of \cite{van Leeuwen2009}; the $B-V$ ({\bf BMV}) values
are from the \textit{Hipparcos} catalog by \cite{Perryman1997};
stellar magnitudes {\bf J}, {\bf H}, and {\bf KS} (i.e.\ $K_{\rm s}$)
are from the 2MASS catalog
\citep{Skrutskie2006} (as reported in SIMBAD) and the {\bf KP} (i.e.\ $K_P$) magnitudes are from the Exoplanet
Archive \citep{Akeson2013}.

@@

%------------------------------------------------------------------------------
% Figure: single planet page
\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../fig/wasp-14b.eps}
\caption{An example page for an individual exoplanet (WASP-14b in this
  case). The numbers listed in each field contain links to the
  reference on NASA ADS. In this example for WASP-14b, we provide the plot
  for the phased RVs, but we have yet to implement such feature for all
  planets with available RV data.}
\label{fig:individual}
\end{figure}

@@

%------------------------------------------------------------------------------
% Figure: single planet page
\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../fig/mass-per-interactive.eps}
\caption{
  An example plot produced by the interactive plotting tools of
  EDE on exoplanets.org. The interactive plotting interface is shown
  on the right, with the mass-period plot shown on the left. The
  $x$-axis is planet orbital period in days and $y$-axis is planet
  mass in Earth's mass. The exoplanet samples being plotted are the
  ones in the EOD, including transit planets (blue large dots), RV
  planets (red triangles), and timing planets (magenta squares). The
  KOIs are plotted as black small dots, and their masses are
  calculated using their radii based on mass-radius relations from the
  literature (see Section~\ref{sec:orbit}).  Note the
  apples-to-oranges comparison enabled by the hybrid MASS field on the y-axis, which blends estimated
  masses, minimum masses, and true masses on a single plot.}
\label{fig:koi}
\end{figure}

\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../fig/senew.eps}
\caption{An example plot that demonstrates the current secondary
  eclipse measurements. Each planet has a set of circles that stand
  for its available secondary eclipse measurements in the database,
  including \spitzer\ 8.0, 5.8, 4.5, \& 3.6 \micron, and ground-based
  $J$, $H$, and $K_{\rm s}$ bands. \kepler\ secondary eclipse measurements
  are labeled as solid black dots. A few representative planets are
  also annotated (a feature not offered by the EDE Plotter, but
  trivially implemented by other image or presentation software).}
\label{fig:se}
\end{figure}
